TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Added sources

The tests conducted with the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. \texttt{netem} is applied to the incoming side of the interfaces of the clients to emulate the same packet loss and delay. Windows, which is tested as a server, does not support \texttt{netem}. Therefore the packet loss and delay are applied to the incoming interfaces of the clients. Packet loss and delay are chosen as the behavior of most TCP algorithms depends on those variables [TODO: SRC]. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

>>>>

The tests conducted with the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. \texttt{netem} is applied to the incoming side of the interfaces of the clients to emulate the same packet loss and delay. Windows, which is tested as a server, does not support \texttt{netem}. Therefore the packet loss and delay are applied to the incoming interfaces of the clients. Packet loss and delay are chosen as the behavior of most TCP algorithms depends on those variables \cite{bbr-congestion}\cite{bic-tcp-congestion}\cite{compound-tcp-congestion}\cite{cubic-tcp-congestion}\cite{dctcp-congestion}. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.
